Supplement: Bootstrapping Domain Specific Languages for Bayesian Program Learning

### 2018-02-09 supplement.tex
reorganize DSL listings

\vfill\null\columnbreak

\section{Initial domain-specific languages}
\subsection{List functions}
DSL for the list function experiment domain is shown below. The lower
section with seven primitives designates those given to the \emph{rich} DSL
variant and not the \emph{base} variant. The rich variant is not supplied
the \texttt{if} primitive, because its primary intention is to enable the
learning of the \texttt{filter}, \texttt{index}, and \texttt{slice}
concepts.

\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & [$\alpha$] \\
    singleton & $\alpha$ $\rightarrow$ [$\alpha$] \\
    concat & [$\alpha$] $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$] \\
    mapi & (int $\rightarrow$ $\alpha$ $\rightarrow$ $\beta$) \\
    & \qquad\qquad$\rightarrow$ [$\alpha$] $\rightarrow$ [$\beta$] \\
    reducei & ($\beta$ $\rightarrow$ int $\rightarrow$ $\alpha$ $\rightarrow$ $\beta$)\\
    & \qquad\qquad$\rightarrow$ $\beta$ $\rightarrow$ [$\alpha$] $\rightarrow$ $\beta$ \\
    \hline
    true & bool \\
    not & bool $\rightarrow$ bool \\
    and & bool $\rightarrow$ bool $\rightarrow$ bool \\
    or & bool $\rightarrow$ bool $\rightarrow$ bool \\
    if & bool $\rightarrow$ $\alpha$ $\rightarrow$ $\alpha$ $\rightarrow$ $\alpha$ \\
    \hline
    0 $\cdots$ 5 & int \\
    + & int $\rightarrow$ int $\rightarrow$ int \\
    * & int $\rightarrow$ int $\rightarrow$ int \\
    negate & int $\rightarrow$ int \\
    mod & int $\rightarrow$ int $\rightarrow$ int \\
    eq? & int $\rightarrow$ int $\rightarrow$ bool \\
    gt? & int $\rightarrow$ int $\rightarrow$ bool \\
    is-prime & int $\rightarrow$ bool \\
    is-square & int $\rightarrow$ bool \\
    range & int $\rightarrow$ [int] \\
    sort & [int] $\rightarrow$ [int] \\
    \hline
    sum & [int] $\rightarrow$ int \\
    reverse & [$\alpha$] $\rightarrow$ [$\alpha$] \\
    all & ($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool \\
    any & ($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool \\
    index & int $\rightarrow$ [$\alpha$] $\rightarrow$ $\alpha$ \\
    filter & ($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$] \\
    slice & int $\rightarrow$ int $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$] \\
  \hline
\end{tabular}
\end{center}

\subsection{Boolean circuits}
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    nand & $\text{bool}\to \text{bool}\to \text{bool}$ \\  \hline
\end{tabular}
\end{center}

@@

\subsection{String editing}
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
  0&$\mathbb{Z}$\\
  +1&$\mathbb{Z}\to \mathbb{Z}$\\
  -1&$\mathbb{Z}\to \mathbb{Z}$\\
  split&$\text{char}\to \text{string}\to \left[\text{string} \right]$\\
  join&$\text{string}\to \left[\text{string} \right]\to \text{string}$\\
  map&$(\text{string}\to \text{string})\to \left[\text{string} \right]\to \left[\text{string} \right]$\\
  nth&$\mathbb{Z}\to \left[\text{string} \right]\to \text{string}$\\
  slice&$\mathbb{Z}\to \mathbb{Z}\to \text{string}\to \text{string}$\\
  length&$\text{string}\to \mathbb{Z}$\\
  chr->str&$\text{char}\to \text{string}$\\
  trim&$\text{string}\to \text{string}$\\
  upper&$\text{string}\to \text{string}$\\
  lower&$\text{string}\to \text{string}$\\
  capitalize&$\text{string}\to \text{string}$\\\hline
\end{tabular}
\end{center}
We also provide the constant empty string which has type string and also provide
constant characters which have the type char.

>>>>

\section{Initial domain-specific languages}
\subsection{Boolean circuits}
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    nand & $\text{bool}\to \text{bool}\to \text{bool}$ \\  \hline
\end{tabular}
\end{center}

@@

\subsection{String editing}
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
  0&$\mathbb{Z}$\\
  +1&$\mathbb{Z}\to \mathbb{Z}$\\
  -1&$\mathbb{Z}\to \mathbb{Z}$\\
  split&$\text{char}\to \text{string}\to \left[\text{string} \right]$\\
  join&$\text{string}\to \left[\text{string} \right]\to \text{string}$\\
  map&$(\text{string}\to \text{string})$\\
  &$\qquad\quad\to\left[\text{string} \right]\to \left[\text{string} \right]$\\
  nth&$\mathbb{Z}\to \left[\text{string} \right]\to \text{string}$\\
  slice&$\mathbb{Z}\to \mathbb{Z}\to \text{string}\to \text{string}$\\
  length&$\text{string}\to \mathbb{Z}$\\
  chr->str&$\text{char}\to \text{string}$\\
  trim&$\text{string}\to \text{string}$\\
  upper&$\text{string}\to \text{string}$\\
  lower&$\text{string}\to \text{string}$\\
  capitalize&$\text{string}\to \text{string}$\\\hline
\end{tabular}
\end{center}
We also provide the constant empty string which has type string and also provide
constant characters which have the type char.

\subsection{List functions}
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & [$\alpha$] \\
    singleton & $\alpha \to$ [$\alpha$] \\
    concat & [$\alpha$] $\to$ [$\alpha$] $\to$ [$\alpha$] \\
    mapi & $(\mathbb{Z} \to \alpha \to \beta)$ \\
    & \qquad\qquad$\to$ [$\alpha$] $\to$ [$\beta$] \\
    reducei & $(\beta \to \mathbb{Z} \to \alpha \to \beta)$\\
    & \qquad\qquad$\to \beta \to$ [$\alpha$] $\to \beta$ \\
    \hline
    if & bool $\to \alpha \to \alpha \to \alpha$ \\
    \hline
    true & bool \\
    not & bool $\to$ bool \\
    and & bool $\to$ bool $\to$ bool \\
    or & bool $\to$ bool $\to$ bool \\
    0 $\cdots$ 5 & $\mathbb{Z}$ \\
    + & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    * & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    negate & $\mathbb{Z} \to \mathbb{Z}$ \\
    mod & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    eq? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    gt? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    is-prime & $\mathbb{Z} \to$ bool \\
    is-square & $\mathbb{Z} \to$ bool \\
    range & $\mathbb{Z} \to$ [$\mathbb{Z}$] \\
    sort & [$\mathbb{Z}$] $\to$ [$\mathbb{Z}$] \\
    \hline
    sum & [$\mathbb{Z}$] $\to \mathbb{Z}$ \\
    reverse & [$\alpha$] $\to$ [$\alpha$] \\
    all & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ bool \\
    any & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ bool \\
    index & $\mathbb{Z} \to$ [$\alpha$] $\to \alpha$ \\
    filter & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ [$\alpha$] \\
    slice & $\mathbb{Z} \to \mathbb{Z} \to$ [$\alpha$] $\to$ [$\alpha$] \\
  \hline
\end{tabular}
\end{center}
The lower section with seven primitives designates those given to the
\emph{rich} DSL variant and not the \emph{base} variant. The rich variant is
not supplied the \texttt{if} primitive, because its primary intention is to
enable the learning of the \texttt{filter}, \texttt{index}, and
\texttt{slice} concepts. Greek letters represent polymorphic types.
